Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-07 paper-correlations.tex
Remove dubious sentences
Change caption to the figure with line segments

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/cf_1.png}
  \caption[]{A schematic representation of a binary porous media (pores are
    shaded) with examples of CFs computations (all classical correlation
    functions are presented according to the legend on the right
    side). Computations are results of individual events (producing either 0 or
    1) ensemble averaged over the image, direction or represented as full
    correlation map.}
  \label{fig:functions}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/cf_1.png}
  \caption[]{A schematic representation of a binary porous media (pores are
    shaded) with examples of CFs computations (all classical correlation
    functions are presented according to the legend on the right
    side). Computations take into account all possible configurations of a line
    segment (or a N-dimensional ball for pore size function) which either make a
    contribution to the CF (conventionally shown as ``CF = 1'') or do not make a
    contribution (``CF = 0'').}
  \label{fig:functions}
\end{figure}
